%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Fullstack Elixir developer} % Job title
    {Curiosum} % Organization
    {Remote} % Location
    {Jun 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on various outsourced projects across different industries.}
        \item {Handled both frontend and backend development.}
        \item {Worked on an E-learning platform for professionals}
        \begin{itemize}[leftmargin=3.0mm,labelsep=0.8mm,label={--}]
          \item {Built an interactive e-learning system using LiveView.}
          \item {Designed dynamic UIs and handled state management for a seamless user experience.}
          \item {Optimized queries and backend logic for improved performance.}
        \end{itemize}
        \item {Developed an HR \& Payroll Integration App}
        \begin{itemize}[leftmargin=3.0mm,labelsep=0.8mm,label={--}]
          \item {Created a REST API to connect multiple HR and payroll platforms.}
          \item {Implemented OpenAPI specs for better API documentation and integration.}
          \item {Improved data flow between systems, reducing processing time}
        \end{itemize}
        \item {Contributed to MedTech Platforms }
        \begin{itemize}[leftmargin=3.0mm,labelsep=0.8mm,label={--}]
          \item {Built a LiveView interface for a medical platform, ensuring secure real-time interactions.}
          \item {Developed a REST API backend for a medtech system.}
          \item {Ensured compliance with industry security standards and best practices.}
        \end{itemize}
        \item {Contributed to an open source user-friendly translations manager}
      \end{cvitems}
    }

  \vspace{3.5mm}

  \cventry
    {Web developer - Intern} % Job title
    {BlueRider.Software} % Organization
    {Białystok, Poland} % Location
    {Jul 2021 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a webapp for managing a collection of boardgames}
        \item {Built REST API with Django RESTFramework.}
        \item {Built a frontend to a REST API with Vue.js.}
        \item {Built fully automated CI/CD pipelines on JenkinsCI and Gitlab CI for containerized applications using Docker and docker‑compose.}
      \end{cvitems}
    }
%--------------------------------------------------------

\end{cventries}
